Sequence-to-sequence Architecture\\Using BERT

### 2020-06-25 paper/paper.tex
Load small dataset
Update paper

\frenchspacing
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
\pdfinfo{
    /Title (Sequence-to-sequence Architecture Using BERT)
    /Author (Claudio Scheer, Jos\'e Fernando Possebon)
}
\setcounter{secnumdepth}{0}
\begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Sequence-to-sequence Architecture\\Using BERT}
\author{Claudio Scheer \and Jos\'e Fernando Possebon\\
    Pontifical Catholic University of Rio Grande do Sul - PUCRS\\
    claudio.scheer@edu.pucrs.br,
    jose.possebon@edu.pucrs.br
}

@@

\cite{DBLP:journals/corr/BahdanauCB14} - Proposed attention

\cite{DBLP:journals/corr/VaswaniSPUJGKP17} - Attention is all you need

@@

\cite{DBLP:journals/corr/abs-1810-04805} - BERT

Similarly to the original sequence-to-sequence model using a recurrent neural network, the model discussed in this paper uses two BERT neural network: one neural network to encode the input and another to decode the input encoded.

@@

@@

>>>>

\frenchspacing
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
\pdfinfo{
    /Title (Sequence-to-sequence Architecture Using BERT)
    /Author (Claudio Scheer, Jos\'e Fernando Possebon)
}
\setcounter{secnumdepth}{0}
\begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Sequence-to-sequence Architecture\\Using BERT}
\author{Claudio Scheer \and Jos\'e Fernando Possebon\\
    Pontifical Catholic University of Rio Grande do Sul - PUCRS\\
    \{claudio.scheer, jose.possebon\}@edu.pucrs.br
}

@@

 - Attention is all you need

@@

BERT is a short for Bidirectional Encoder Representations from Transformers, proposed by \cite{DBLP:journals/corr/abs-1810-04805}. Transformers network was proposed by \cite{DBLP:journals/corr/VaswaniSPUJGKP17} and use the attentions mechanism, proposed by \cite{DBLP:journals/corr/BahdanauCB14}, to learn representations between words that can express their contextual meaning.

The original BERT model was pre-trained in a corpus comprising Wikipedia and Book Corpus. BERT has two pre-trained models available: BERT large, with \num{345}{M} parameters (24 layers) and BERT base, with \num{110}{M} (12 layers).

The model was pre-trained for masked language modeling nas next sentence predictions tasks. However, with the replacement of the last layer and fine-tuning, the model can be used for other tasks, using the same parameters as the original BERT model.

@@

The \texttt{BertModel} class provided by Hugging Face can behave as an encoder or decoder. The difference is that, for the encoder, only a layer of self-attention is used and, for decoder, a layer of cross-attention is added between the layers of self-attention. In a nutshell, the difference is that self-attention is only applied to the input sequence, while cross-attention is applied to the input and output sentences.

we used the bert base

@@

The evaluation of the model was
